Paper notes

### 2019-08-08 paper_notes.Rmd
test utility added
added functions overlapping

library(Hmisc)

@@

@@

>>>>

library(Hmisc)
library(ggplot2)

@@

```{r graph function include=TRUE, echo=FALSE}

f0s <- f_eth(i_e,M,0,n,S)
f1s <- f_eth(i_e,M,1,n,S)
f2s <- f_eth(i_e,M,2,n,S)
f3s <- f_eth(i_e,M,3,n,S)
f4s <- f_eth(i_e,M,4,n,S)
f5s <- f_eth(i_e,M,5,n,S)
f6s <- f_eth(i_e,M,6,n,S)
f7s <- f_eth(i_e,M,7,n,S)
f8s <- f_eth(i_e,M,8,n,S)

i_e = 0.5
M = 1
S = 1
n = 8

f0c <- f_eth(i_e,M,0,n,S)
f1c <- f_eth(i_e,M,1,n,S)
f2c <- f_eth(i_e,M,2,n,S)
f3c <- f_eth(i_e,M,3,n,S)
f4c <- f_eth(i_e,M,4,n,S)
f5c <- f_eth(i_e,M,5,n,S)
f6c <- f_eth(i_e,M,6,n,S)
f7c <- f_eth(i_e,M,7,n,S)
f8c <- f_eth(i_e,M,8,n,S)

i_e = 0.5
M = 1
S = 0
n = 8

f0t <- f_eth(i_e,M,0,n,S)
f1t <- f_eth(i_e,M,1,n,S)
f2t <- f_eth(i_e,M,2,n,S)
f3t <- f_eth(i_e,M,3,n,S)
f4t <- f_eth(i_e,M,4,n,S)
f5t <- f_eth(i_e,M,5,n,S)
f6t <- f_eth(i_e,M,6,n,S)
f7t <- f_eth(i_e,M,7,n,S)
f8t <- f_eth(i_e,M,8,n,S)

Utility_S <- c(f0s,f1s,f2s,f3s,f4s,f5s,f6s,f7s,f8s)
Utility_C <- c(f0c,f1c,f2c,f3c,f4c,f5c,f6c,f7c,f8c)
Utility_T <- c(f0t,f1t,f2t,f3t,f4t,f5t,f6t,f7t,f8t)

# name_E <- paste0("Desired proportion i = ",i_e,"; M = ",M,"; S = ",S)
# plot(num_sim_col,Utility_T, xlab = "Similar ethnics neighborhood j", ylab = "Ethnic Utility",  main = "Ethnic Utility for neighborhood j of agent i",  sub = name_E)
# report_E <- paste0("M = ",M,"; S = ",S,"; Desired proportion i = ",i_e,"; Similar ethnics neighborhood j = ", seq(0, 8, by = 1), "; Utility ij = ", Utility_T)
# print(report_E)

# func_type <- c(rep("symmetric",9),rep("constant",9),rep("threshold",9))

x_graph <- rep(seq(0, 8, by = 1),3)
funct_symm <- c(rep("symmetric",9),rep("constant",9),rep("threshold",9))
utility_location <- c(Utility_S,Utility_C,Utility_T)

A <- data.frame(x_graph,utility_location,funct_symm)

A

write.csv2(A,file="C:/Users/rocpa/OneDrive/Desktop/08_08_2019/ethnic-value_multinomial/data_utility")

A_graph <- ggplot(A,aes(x_graph,utility_location))

A_graph + geom_point(aes(colour = funct_symm, shape= funct_symm, size = funct_symm)) + scale_size_manual(values = c(4,5,3)) + scale_shape_manual(values = c(19,19,19)) + scale_color_manual(values = c("darkorchid","forestgreen","black"))

```{r overlap_function include=TRUE, echo=FALSE}

x_graph_overlap <- rep(seq(0, 100, by = 12.5),4)

S_0 <- c(0,0,0,0,0,NA,NA,NA,NA)
M_1 <- c(NA,NA,NA,NA,1,1,1,1,1)
S_1 <- c(0,0.25,0.5,0.75,1,NA,NA,NA,NA)
M_0 <- c(NA,NA,NA,NA,1,0.76,0.5,0.24,0)  # should be 0.75 and 0.24, I think due to round(U)2 in the function

funct_overlap <- c(rep("S = 0",9),rep("M = 1",9),rep("S = 1",9),rep("M = 0",9))
utility_overlap <- c(S_0,M_1,S_1,M_0)

overlap <- data.frame(x_graph_overlap,utility_overlap,funct_overlap)

# overlap

graph_overlap <- ggplot(overlap,aes(x_graph_overlap,utility_overlap))

suppressWarnings(print(
graph_overlap + geom_line(aes(colour = funct_overlap)) + scale_color_manual(values = c("red","forestgreen","black","purple"),name = "Parameters Setting") + theme_bw() + labs(x = "percentage similars",y = "utility for location")
))

@@

i_e = 0.5
M = 0
S = 1
n = 7
